Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 results.tex
spell check
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@983 ccdd05d5-56c1-461a-bf98-85f6876523b4

We expect two known contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ basis and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of resampling that cause signal loss.  The \SNR\ loss is to be
compared with the mismatch of 0.03 that arises from the discreteness of the
template bank.  We will consider a target \SNR\ loss to be a factor of 10
smaller than this, i.e., no more than $\sim$0.003.

@@

In this section we check the effect of the \SVD\ tolerance parameter defined
in~\cite{Cannon:2010p10398}.  By changing the tolerance of the reconstruction
of the physical waveforms one directly affects the mismatch that results from
the truncation of the orthogonal filter matrix.  The conditions presented here
are more complicated than in the original work~\cite{Cannon:2010p10398} due to
the inclusion of the time-sliced templates and resampling.  Figure~%
\ref{fig:hist-svd-tolerance} demonstrates that it is possible to achieve
typical \SNR\ losses of $\ll1\%$.  However, we do notice that the mismatch
saturates with respect to the tolerance.  This could be the effect of the
resampling, or another \SNR\ loss that we did not model or expect.  However the
saturation is still an order of magnitude below our target mismatch of
$\sim$0.003.  We find that an \SVD\ tolerance of $\left(1-10^{-4}\right)$ is
adequate to acheive our target \SNR{} loss.
%
\begin{figure}
	\begin{center}
		\subfloat[Mismatch versus \textsc{svd} tolerance]{\label{fig:hist-svd-tolerance}\includegraphics{bw.pdf}}
		\subfloat[Mismatch versus $N^\shortuparrow$]{\label{fig:hist-interpolate}\includegraphics{bw_resample.pdf}}
		\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse respones.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
\subref{fig:hist-svd-tolerance} the interpolation filter length is held fixed
at $N^\shortuparrow = 192$, while the \SVD\ tolerance is varied from
$\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  In \subref{fig:hist-interpolate}, the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$ is varied from 8 to 192 coefficients.}
	\end{center}
\end{figure}

>>>>

We expect two known contributions to the \SNR\ loss to arise in our
implementation of the \lloid\ algorithm.  The first is the \SNR\ loss due to
the truncation of the \SVD\ basis and estimates for it
exist~\cite{Cannon:2010p10398}.  The second comes from non ideal
implementations of re-sampling that cause signal loss.  The \SNR\ loss is to be
compared with the mismatch of 0.03 that arises from the discreteness of the
template bank.  We will consider a target \SNR\ loss to be a factor of 10
smaller than this, i.e., no more than $\sim$0.003.

@@

In this section we check the effect of the \SVD\ tolerance parameter defined
in~\cite{Cannon:2010p10398}.  By changing the tolerance of the reconstruction
of the physical waveforms one directly affects the mismatch that results from
the truncation of the orthogonal filter matrix.  The conditions presented here
are more complicated than in the original work~\cite{Cannon:2010p10398} due to
the inclusion of the time-sliced templates and re-sampling.  Figure~%
\ref{fig:hist-svd-tolerance} demonstrates that it is possible to achieve
typical \SNR\ losses of $\ll1\%$.  However, we do notice that the mismatch
saturates with respect to the tolerance.  This could be the effect of the
re-sampling, or another \SNR\ loss that we did not model or expect.  However the
saturation is still an order of magnitude below our target mismatch of
$\sim$0.003.  We find that an \SVD\ tolerance of $\left(1-10^{-4}\right)$ is
adequate to achieve our target \SNR{} loss.
%
\begin{figure}
	\begin{center}
		\subfloat[Mismatch versus \textsc{svd} tolerance]{\label{fig:hist-svd-tolerance}\includegraphics{bw.pdf}}
		\subfloat[Mismatch versus $N^\shortuparrow$]{\label{fig:hist-interpolate}\includegraphics{bw_resample.pdf}}
		\caption{Box-and-whisker plot of mismatch between nominal
template bank and \lloid\ measured impulse responses.  The upper and lower boundaries of
the boxes show the upper and lower quartiles; the lines in the center denote the medians.
The whiskers represent the minimum and maximum mismatch over all templates.  In 
\subref{fig:hist-svd-tolerance} the interpolation filter length is held fixed
at $N^\shortuparrow = 192$, while the \SVD\ tolerance is varied from
$\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  In \subref{fig:hist-interpolate}, the \SVD\ tolerance is fixed at $\left(1-10^{-6}\right)$ while $N^\shortuparrow$ is varied from 8 to 192 coefficients.}
	\end{center}
\end{figure}
